Delone lattice studies in \CIII, the space of three complex variables

### 2022-12-22 C3/C3.tex
fixing matrix to use booktabs
playing with a n extra line in the table. Goes away if the table environment is removed. Goes away in preprint mode.

\documentclass[]{iucr}              % DO NOT DELETE THIS LINE
%\documentclass[]{iucr}              % DO NOT DELETE THIS LINE
\usepackage{amssymb}
\usepackage[fleqn]{amsmath}
%\usepackage{bm}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{booktabs}
%\usepackage{calligra}
\usepackage{array}
\DeclareMathAlphabet{\mathcalligra}{T1}{calligra}{m}{n}
\def\mathbi#1{\textbf{\em #1}}
\numberwithin{equation}{section}
%\DeclareMathSymbol{\Gamma}{\mathalpha}{letters}{"00}
%\DeclareMathSymbol{\Lambda}{\mathalpha}{letters}{"03}
%\DeclareMathSymbol{\Omega}{\mathalpha}{letters}{"0A}
%\DeclareMathAlphabet{\mathitbf}{OML}{cmm}{b}{it}
\hyphenation{Niggli}
\def\mathbi#1{\textbf{\em #1}}
%\numberwithin{equation}{section}
%\DeclareMathSymbol{\Gamma}{\mathalpha}{letters}{"00}
%\DeclareMathSymbol{\Lambda}{\mathalpha}{letters}{"03}
%\DeclareMathSymbol{\Omega}{\mathalpha}{letters}{"0A}
%\DeclareMathAlphabet{\mathitbf}{OML}{cmm}{b}{it}
\usepackage{color}
\usepackage{ulem}
\usepackage{url}
\usepackage{yfonts}
%\usepackage{xr-hyper}
%\usepackage[draft]{hyperref}
%\usepackage{bibentry}
\newcommand{\SVI}[0]{$\bf{S^{6}}$}
\newcommand{\GVI}[0]{$\bf{G^{6}}$}
\newcommand{\CIII}[0]{$\bf{C^{3}}$}
\newcommand{\DVII}[0]{$\bf{D^{7}}$}
\newcommand{\VVII}[0]{$\bf{V^{7}}$}

@@

	\end{abstract}

	%-------------------------------------------------------------------------
	% The main body of the paper
	%-------------------------------------------------------------------------
	% Now enter the text of the document in multiple \section's, \subsection's
	% and \subsubsection's as required.

	% Appendices appear after the main body of the text. They are prefixed by
	% a single \appendix declaration, and are then structured just like the
	% body text.

@@

	Next we define the operators in \CIII{} t
	hat will be used in the matrix descriptions of 
	the transformations at the boundaries of the fundamental unit.\\

\begin{table}	
	\begin{tabular}{|l|l|l|l|}
\toprule
	Operator
						&Usage	
													&Result	
																			&Name\\
\midrule
	$\Minus{}_r $		&  $\Minus{}_r(c_j)$ 		& $(-x_j, -x_j+y_j)$ 	& Minus real \\ 
	$\Minus{}_i $ 		& $\Minus{}_i(c_j)$ 		& $(x_j-y_j,-y_j) $ 	& Minus imag\\ 
	$\textfrak{P}_r$ 	& $ \textfrak{P}_r(c_j)$ 	& $(x_j, x_j)$ 			& Plus real\\ 
	$\textfrak{P}_i$ 	&  $\textfrak{P}_i(c_j)$  	& $(y_j, y_j)$ 			& Plus imag\\ 
	$\Real$ 			&  $\Real(c_j)$ 			& $x_j$ 				& Real \\ 
	$\Imaginary$ 		&  $\Imaginary(c_j)$ 		& $y_j$ 				& Imaginary\\
\bottomrule
	\end{tabular}

\end{table}

>>>>

\documentclass[preprint]{iucr}              % DO NOT DELETE THIS LINE
%\documentclass[]{iucr}              % DO NOT DELETE THIS LINE
\usepackage{amssymb}
\usepackage[fleqn]{amsmath}
%\usepackage{bm}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{booktabs}
%\usepackage{calligra}
\usepackage{array}
\DeclareMathAlphabet{\mathcalligra}{T1}{calligra}{m}{n}
\def\mathbi#1{\textbf{\em #1}}
\numberwithin{equation}{section}
%\DeclareMathSymbol{\Gamma}{\mathalpha}{letters}{"00}
%\DeclareMathSymbol{\Lambda}{\mathalpha}{letters}{"03}
%\DeclareMathSymbol{\Omega}{\mathalpha}{letters}{"0A}
%\DeclareMathAlphabet{\mathitbf}{OML}{cmm}{b}{it}
\hyphenation{Niggli}
\def\mathbi#1{\textbf{\em #1}}
%\numberwithin{equation}{section}
%\DeclareMathSymbol{\Gamma}{\mathalpha}{letters}{"00}
%\DeclareMathSymbol{\Lambda}{\mathalpha}{letters}{"03}
%\DeclareMathSymbol{\Omega}{\mathalpha}{letters}{"0A}
%\DeclareMathAlphabet{\mathitbf}{OML}{cmm}{b}{it}
\usepackage{color}
\usepackage{ulem}
\usepackage{url}
\usepackage{yfonts}
%\usepackage{xr-hyper}
%\usepackage[draft]{hyperref}
%\usepackage{bibentry}
\newcommand{\SVI}[0]{$\bf{S^{6}}$}
\newcommand{\GVI}[0]{$\bf{G^{6}}$}
\newcommand{\CIII}[0]{$\bf{C^{3}}$}
\newcommand{\DVII}[0]{$\bf{D^{7}}$}
\newcommand{\VVII}[0]{$\bf{V^{7}}$}

@@

	\end{abstract}
	% Appendices appear after the main body of the text. They are prefixed by
	% a single \appendix declaration, and are then structured just like the
	% body text.

@@

	Next we define the operators in \CIII{} t
	hat will be used in the matrix descriptions of 
	the transformations at the boundaries of the fundamental unit.\\
	See Table \ref{tab:operators}.

\begin{table}	
	\label{tab:operators}
	\begin{tabular}{c l l l }
\toprule
	Operator
						&Usage	
													&Result	
																			&Name\\
\midrule
	$\Minus{}_r $		&  $\Minus{}_r(c_j)$ 		& $(-x_j, -x_j+y_j)$ 	& Minus real \\ 
	$\Minus{}_i $ 		& $\Minus{}_i(c_j)$ 		& $(x_j-y_j,-y_j) $ 	& Minus imag\\ 
	$\textfrak{P}_r$ 	& $ \textfrak{P}_r(c_j)$ 	& $(x_j, x_j)$ 			& Plus real\\ 
	$\textfrak{P}_i$ 	&  $\textfrak{P}_i(c_j)$  	& $(y_j, y_j)$ 			& Plus imag\\ 
	$\Real$ 			&  $\Real(c_j)$ 			& $x_j$ 				& Real \\ 
	$\Imaginary$ 		&  $\Imaginary(c_j)$ 		& $y_j$ 				& Imaginary\\

\bottomrule
	\end{tabular}		
\end{table}
